---
title: "Untitled"
author: Yue Chen
output: github_document
---

## Problem 1

```{r}
library(tidyverse)
```

Create a data frame with the specified elements.

```{r}
df1 = tibble(
  samp = rnorm(10),
  char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
  samp_gt_0 = samp > 0,
  factor_vec = factor(c("A", "B", "C", "A", "B", "C", "A", "B", "C", "A")))   
```

Take the mean of each variable in data frame.

```{r}
mean(pull(df1, samp))
mean(pull(df1, samp_gt_0))
mean(pull(df1, char_vec))
mean(pull(df1, factor_vec))
```

I can take the mean of numbers and logical vectors but not character or factor.

```{r}
as.numeric(pull(df1, samp))
as.numeric(pull(df1, samp_gt_0))
as.numeric(pull(df1, char_vec))
as.numeric(pull(df1, factor_vec))
```


Convert logical vector to numeric, and multiply the random sample by the result.

```{r}
as.numeric(pull(df1,samp_gt_0)) * pull(df1, samp)
```


Convert logical vector to a factor, and multiply the random sample by the result.

```{r}
as.factor(pull(df1,samp_gt_0)) * pull(df1, samp)
```

I cannot multiply a factor to numbers.

Convert logical vector to a factor and then convert the result to numeric, and multiply the random sample by the result

```{r}
as.numeric(as.factor(pull(df1, samp_gt_0))) * pull(df1, samp)

```


## Problem 2
```{r}
data("penguins", package = "palmerpenguins")

```

```{r}
summary(penguins)
```


The data frame contains `r ncol(penguins)` variables including `r names(penguins)` of `r nrow(penguins)` penguins. Species is a `r class(pull(penguins, species))` vector, with levels `r levels(pull(penguins, species))`. Island is a `r class(pull(penguins, island))` vector, with levels `r levels(pull(penguins, island))`. Bill_length_mm is a `r class(pull(penguins, bill_length_mm))` vector, with range of `r range(pull(penguins, bill_length_mm), na.rm = TRUE)` mm and mean of `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)` mm. Bill_depth_mm is a `r class(pull(penguins, bill_depth_mm))` vector, with range of `r range(pull(penguins, bill_depth_mm), na.rm = TRUE)` mm and mean of `r mean(pull(penguins, bill_length_mm), na.rm = TRUE)` mm. Flipper_length_mm is a `r class(pull(penguins, flipper_length_mm))` vector, with range of `r range(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm and mean of `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)` mm. Body_mass_g is a `r class(pull(penguins, body_mass_g))` vector, with range of `r range(pull(penguins, body_mass_g), na.rm = TRUE)` g and mean of `r mean(pull(penguins, body_mass_g), na.rm = TRUE)` g.
There were 165 female penguins  and 168 penguins. 11 penguins' sex are unknown. 


```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
```
```{r}
ggsave("scatterplot1.pdf")
```
